### 2023-02-22 text/ManuscriptDraft.Rmd
Editions to manuscript

Evaluating detection performance Since YOLOv5+SAHI has a different
output format than YOLOv5 on its own, customs scripts were created to 1)
translate YOLOv5 output pickle files to standard YOLOv5 text files and
2) calculate detection performance variables (precision and recall) for
both methods. Precision is the number of correct predictions out of all
predictions made. Recall is the proportion of the true number of objects
that were detected by the model. F1 is the weighted average of precision
and recall. A value of 0.3 was used as the IOU threshold for whether
bounding boxes overlapped sufficiently to be considered correct.

@@

@@

The model trained on the 640x640 pixel images reached best validation
accuracy at epoch 505. The model trained on the 1280x1280 pixel images
reached best validation accuracy at epoch 705. Table 1 Detection
accuracy with the different models. Method (IOU 0.3) Precision Recall F1
YOLOv5 640 0.46 0.19 0.27 YOLOv5 640 + SAHI (128) 0.60 0.12 0.20 YOLOv5
1280 0.54 0.56 0.55 YOLOv5 1280 + SAHI (128) 0.63 0.41 0.50

Table 2 Detection accuracy of YOLOv5 1280 + SAHI with different window
sizes for the SAHI slicing (256, 128, 64). Model 1280 SAHI 256 SAHI 128
SAHI 64 IOU 0.3 Precision Recall Precision Recall Precision Recall 0.57
0.47 0.63 0.41 0.66 0.41

Fig. 1 Example of image with challenging background. Result from model
640 + SAHI 128. For this image, the precision was 0.16 and the recall
0.83.

@@

Table 3 Variation in performance between images (YOLOv5 1280 + SAHI
128). Image Precision Recall A11.1 0.78 1.0 A17.1 0.54 0.79 A31.1 0.42
0.71 A38.1 0.73 0.50 A49.1 0.10 1.0 A6.1 0.60 0.78 B37.1 0.53 0.39 C3.1
0.48 0.85 C7.3 0.62 0.68 D23.1 0.82 0.44 D4.1 0.20 0.20 D9.1 0.66 0.09

>>>>

Evaluating detection performance

Since YOLOv5+SAHI has a different output format than YOLOv5 on its own,
customs scripts were created to 1) translate YOLOv5 output pickle files
to standard YOLOv5 text files and 2) calculate detection performance
variables (precision and recall) for both methods. Precision is the
number of correct predictions out of all predictions made. Recall is the
proportion of the true number of objects that were detected by the
model. F1 is the weighted average of precision and recall. A value of
0.3 was used as the IOU threshold for whether bounding boxes overlapped
sufficiently to be considered correct.

@@

The model trained on the standard images reached best validation
accuracy at epoch xxx.

@@

The model trained on the sliced images reached best validation accuracy
at epoch xxx.

Running inference on image slices with

Table 1 Detection accuracy with the different models. Method (IOU 0.3)
Precision Recall F1 YOLOv5 640 0.46 0.19 0.27 YOLOv5 640 + SAHI (128)
0.60 0.12 0.20 YOLOv5 1280 0.54 0.56 0.55 YOLOv5 1280 + SAHI (128) 0.63
0.41 0.50

@@

Table 3 Variation in performance between images (YOLOv5 1280 + SAHI
128).

Image Precision Recall
